A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Fix wording

Hence, the following section cover important aspects to keep in mind when
implementing an OBDD framework efficiently, i.e. data structures, how to deal with
the variable ordering problem and \textit{garbage collection}. \tbr

>>>>

Hence, the following sections cover important aspects to keep in mind when
implementing an OBDD framework efficiently, i.e. efficient data structures, how
to possibly approach the variable ordering problem and \textit{garbage collection}.
\tbr
